 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-02-06 paper.Rmd
reordering stuff
paragraph on tours

@@

## Tours

@@

>>>>

A complimentary approach for visualizing structure in high dimensional data
is the tour. A tour is a sequence of projections of a high dimensional dataset
onto a low-dimensional orthonormal basis matrix, that is represented as a dynamic visualization. The sequence of generated bases are interpolated to form the tour path, allowing a user to explore the subspace of projections. A
grand tour corresponds to choosing new bases at random, and can give an
overview of the structure in the data. Instead of picking projections at random, a guided tour can be used to generate a sequence 'interesting' projections
as quantified by an index function. The tour has been used previously 
by @Wickham2015-cx as tool for exploring statistical model fits.

@@

@@

my contribution + design of interface
